---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Attentional Social Media: Mapping the Spaces and Networks of the Fashion Industry"
```

# geographyoffashion

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio)

This repository contains the data and code for our paper:

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

The repository contains all the data and code needed to reproduce the results and figures in our paper. Although we are not able to share the raw Twitter data publicly, the aggregated counts per hexagon for each fashion keyword, with which all the results can be reproduced, are found in `analysis/data/derived_data/`. The steps taken to produce this aggregated dataset can be found in:
- [analysis/00a-hexagonal-grid-prep.Rmd](analysis/00a-hexagonal-grid-prep.md): Preparation of hexagonal global grid
- [analysis/00b-twitter-data-prep.Rmd](analysis/00b-twitter-data-prep.md): Read in raw Twitter data and perform spatial join to hexagonal grid
- [analysis/00c-twitter-data-group-totals.Rmd](analysis/00c-twitter-data-group-totals.md): Calculate odds ratios, diversity metrics and group totals for each hexagonal cell

The steps needed to recreate the figures can be found in:

Our pre-print is online here:

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to download or install

You can download the compendium as a zip from from [this URL](https://github.com/atepoorthuis/geography-of-fashion/archive/master.zip).

Or you can install this compendium as an R package, geographyoffashion, from GitHub with:


```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("atepoorthuis/geography-of-fashion")
```


### Licenses

**Text, figures and data:**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code:** See the [DESCRIPTION](DESCRIPTION) file
