---
title: "Spatial join between tweets and hexagon grid"
author: "Ate Poorthuis"
date: "02/09/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(data.table)
library(bit64)
library(sf)
library(reversegeocoder)
library(geojsonio)
```

## Spatial join between tweets and hexagon grid

Start by reading in the random sample of tweets as well as the clipped hexagons that we created in the previous step. To join tweets to hexagons, we use `reversegeocoder` (https://github.com/atepoorthuis/reversegeocoder) instead of the conventional `sf::st_join` because it is ~10x faster for this particular scenario.

```{r}
hexagons_clipped <- readRDS(here("analysis/data/derived_data/global_hex_grid.rds"))
random_tweets <- fread(here("analysis/data/raw_data/twitter/random-sample/fashion-random.csv"), select = c("id", "lon", "lat", "created_at", "u_followers_count")) %>% 
  st_as_sf(coords = c("lon", "lat"), crs = 4326) %>% 
  st_transform(st_crs(hexagons_clipped))

hexagons_geojson <- geojson_list(hexagons_clipped) %>% unclass()
ctx <- reversegeocoder::rg_load_polygons(hexagons_geojson)

random_tweets$hex <-reversegeocoder::rg_batch_query(ctx, random_tweets %>% st_coordinates(), "hex")

hexagons_joined <- random_tweets %>% 
  st_set_geometry(NULL) %>% 
  group_by(hex) %>% 
  summarise(random = n(), random_fol = sum(u_followers_count)) %>% 
  right_join(., hexagons_clipped, by = "hex")
hexagons_joined[1:5,]
```

We repeat the join to hexagon procedure for each query in our data. Unfortunately, due to Twitter's T&C we cannot share this raw data here. 
```{r}
file_names <- dir(here("analysis/data/raw_data/twitter/fashion/"), pattern =".*csv", full.names = T)


join_to_grid <- function(file, hexagons) {
  name <- file %>% 
    basename() %>% 
    gsub(pattern = ".csv", replacement = "")
  name_fol <- paste0(name, "_fol")

  tweets <- fread(file, select = c("id", "lon", "lat", "created_at", "u_followers_count")) %>% 
    st_as_sf(coords = c("lon", "lat"), crs = 4326) %>% 
    st_transform(st_crs(hexagons_clipped))
  tweets$hex <-reversegeocoder::rg_batch_query(ctx, tweets %>% st_coordinates(), "hex")

  joined <- tweets %>% 
    st_set_geometry(NULL) %>% 
    group_by(hex) %>% 
    summarise(!!name := n(), !!name_fol := sum(u_followers_count)) %>% 
    right_join(., hexagons, by = "hex")
  invisible(joined)
}

join_with_side_effects <- function(f) {
  hexagons_joined <<- join_to_grid(f, hexagons_joined)
  invisible(basename(f))
}

pblapply(file_names, function(f) join_with_side_effects(f))

hexagons_joined <- hexagons_joined %>% 
  mutate_all(replace_na, replace = 0) %>% 
  st_as_sf()

saveRDS(hexagons_joined, here("analysis/data/derived_data/global_hex_joined.rds"))

hexagons_joined[1:5,]
```

